\textbf{Course: Física Teórica I (CDP7600)} \\[0.2cm] {\Large \textbf{Project}: \hspace{0.2cm} \textit{Fibration building blocks of information-processing networks} }

### 2019-10-31 Manuscript/main.tex
fundamental class calculation

A network $G(V, E)$ is completely defined by the sets of the nodes elements $V$ and the set of the edges $E$. The network has $N = |V|$ nodes that can have connections with one another defined by the set $E$, which contains $M = |E|$ ordered pair of nodes, denoting the directed links between the network nodes. Considering the network, we can define a graph partition $\bar{P}$ over $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$, that is
\begin{equation}
	\bar{P} = \bigcup_{i} P_i
\end{equation}
where $P_i$ are the elements of the partition $\bar{P}$, called blocks. Considering this, if we take an additional graph partition $\bar{Q}$ that has the property that all of its blocks are contained in a block of $\bar{P}$, we say that $\bar{Q}$ is a refinement partition of $\bar{P}$.

@@

Finally, having said all that, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm. The partition $\bar{P}$ is defined as one block containing all the other nodes in the network. The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{Q}$ and all the isolated blocks defined at the beginning. Then, we proceed as
\begin{quotation}
	\textbf{Coarsest Refinement Algorithm}: Remove from $L$ its first set $S$. Replace $Q$ by the \textit{I-split($S$, $Q$)}. Whenever a block $B \in Q$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
\end{quotation}
And this process is repeated until the queue $L$ is empty. At this point, the resulted partition $\bar{P}$ represents the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees.

@@

We apply the above algorithm in the genetic regulatory network of the \textit{Escherichia Coli} bacteria. We obtain the genetic E. Coli network through its transcriptional regulatory interactions data, where each gene is regulated by a transcription factor protein. Since a transcription factor production in the cell is regulated by a gene, we can define a directed connection between two genes if a gene regulates the production of a transcriptional factor, which it regulates another gene. Since a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the links between genes can carry different types of messages. Because of that, it is important that the partitioning algorithm accounts the type of message to construct appropriate input-trees for the network fibers partition. Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as number or string names, and also each link with the type of connection between genes.

Considering this context, we explain now how the algorithm should proper be implemented to have an optimal perfomance concerning its runtime complexity. After discussing the data structures necessary to deal correctly with data, we design an algorithm recipe to show all the main steps of the process explained above. Also, anyone can acess our own personal implementation for genetic regulatory networks in the link \url{https://github.com/higorsmonteiro/fiberblocks} on github platform.

Given a directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks. This means that the initial graph partition $P$ is divided in two different partition $P'$ e $P''$, the first one contained all the single-node blocks containing the solitaire nodes $v$ in which $| E^{-1}(\{v\}) | = 0$, and the second one containing initialing a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$. The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps. Even though the blocks of $P'$ are used as refinement sets, $P'$ is not used by the algorithm. Thus, the final partition is the union of $P'$ and the result of the refinement partitioning of $P''$.

After the above preprocessing we define the data structures for the partition $Q$ for its blocks $B$. A partition is a doubly linked list of blocks, which allows that deletion of blocks be made in constante time $O(1)$ as long we have the block memory address during the procedure. A block is just a structure containing indexing data along with a doubly linked list containg all the nodes that belongs to it. Together with a queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm. At the beginning of the algorithm, we enqueue all the blocks of $P'$ e $P''$ to $L$. Then, we start the algorithm initializing a partition $Q = P''$ and by removing the top element set $S$ of $L$, then we apply the \textit{I-split($S$, $Q$)} to identify the input-tree unstable blocks of $Q$ and split them into input-tree stable blocks with respect to  $S$. This way, all the splitted blocks are push to the end of $L$, with exception the largest resulted blocks for each splitted block. As we have mentioned, the algorithm terminates when there is no more sets in $L$. Even though this is the whole algorithm, the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks. In respect to that below we propose the following implementation construction to the splitting function:

\begin{algorithm}[h]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
	\Input{A set $S$ and a partition $\bar{Q}$}
    \Output{Input tree stable partition $\bar{Q}$ with respect to $S$}
	%\KwResult{}
	Initialize $\bar{U}$ as an empty partition\;
	\For{$\forall B \in \bar{Q}$}
	{
		\If{$\exists \ \{ w_i, w_j \} \subseteq B : | E^{-1}(\{w_i\})\cap S | \neq | E^{-1}(\{w_j\})\cap S |$}
		{
			\textit{push} $B$ to $\bar{U}$\;
			Initialize $\bar{T}$ as an empty partition\;
			\For{$\forall w_i \in B$}
			{
				\eIf{$\exists \ X \in \bar{T} : | E^{-1}(\{w_i\})\cap S | = X(E)$ }
				{
					insert $w_i$ in $X$\;

				}
				{
					create a new block $X$\;
					insert $w_i$ in $X$\;
					$X(E) \leftarrow | E^{-1}(\{w_i\})\cap S |$\;
					push block $X$ to $\bar{T}$ 
				}
			}
		}
		\textit{enqueue} all blocks $X \in \bar{T}$ in $L$, except the largest one\;
		\textit{push} all blocks $X \in \bar{T}$ to $\bar{Q}$\;
	}
	\textit{delete} all blocks $B \in \bar{U}$ in $\bar{Q}$
	\caption{\textit{I-split} $(S,\bar{Q}, L)$}
\end{algorithm}

In the algorithm recipe above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output. Besides its list of nodes, a block $X$ has another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$. This way, a node $w$ belonging to the block to be splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm above.

Finally, considering all the discussion above, we can explicit the complete algorithm in just a few steps.

\begin{algorithm}[h]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
	\Input{A network $G(V, E)$}
	%\KwResult{}
	Initialize $S$ as an empty set\;
	Initialize $L$ as an empty queue\;
	Initialize $\bar{P}$, $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
	$B' = \{ \{ w \} \in V : |E^{-1}(\{w\})|=0 \}$\;
	$B'' = \{ v \in V : |E^{-1}(\{v\})| \geq 1 \}$\;
	\textit{push} all $B'$ to $\bar{P'}$\;
	\textit{push} $B''$ to $\bar{P''}$\;
	\textit{enqueue} $B'' \in \bar{P''}$ to $L$\;
	\textit{enqueue} all blocks $B' \in \bar{P'}$ to $L$\;
	$\bar{Q} \leftarrow \bar{P''}$\;
	\While{$|L| \neq 0$}
	{
		$S \leftarrow \text{\textit{dequeue}}(L)$\;
		$\bar{Q} \leftarrow \text{\textit{I-input}}(S, \bar{Q}, L)$
	}
	\caption{Coarsest Refinement Graph Partitioning}
\end{algorithm}

A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E. Coli} prepared data and another examples. Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.

@@

Using the algorithm above, we applied it to a set of networks examples before its proper application on the \textit{Escherechia Coli} genetic regulatory network data. The reason for that is merely to show that the not just the algorithmic approach chosen is consistent but the written code per si is correctly implementated. For each network, we have a adjacency list containing all the directed connections between the nodes and for each connection we have a string defining the type of regulation of a specific link, where here, considering the genetic regulation context, the types can be positive, negative or dual. The first three examples are all small networks, containing at most $48$ nodes, and so all can be used to test the correctness of the algorithm applied. For that three examples we show the network drawing and their fibers distribution identified as the result of the algorithm.

The first example is showed at the figure \ref{fig:result1}. This network is disconnected, containing two main weakly connected components, and contains only positive regulation between the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type. In this case, we find five non-trivial fibers, that is, fibers with size larger than one.

\begin{figure}[h]
	\centering
	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1.png}}}
	\qquad
	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1-1.png}}}
	\caption{}
	\label{fig:result1}
\end{figure}

At the end of the algorithm, all the fibers identified are input-tree stable with respect to all fibers in the network, including the fiber itself. Then, labelling each fiber by an index or color we can then construct the fibration building blocks through the calculation of the fundamental class number $n$ and through the subclass number $l$. Again, a fibration building block is defined as the nodes inside the fiber as well as the $l$ external nodes that directly regulates at least one node of the current fiber. By that, we calculate the fundamental class number $n_k$ of the fiber $k$ by constructing the adjacency matrix $A_{ij}^{k}$ of its fibration building block and then calculating the largest eigenvalue of it. The value of $n$ quantifies the information loops of the fibration building blocks and can be either a integer or fractal golden ration.

Labelling the resulted fiber distribution, we obtain the following fibration classification for each fibratiion buuilding block of the network containing more than one node:

\begin{figure}[!ht]
    \centering
    \subfloat[]{{\includegraphics[scale=0.22]{Figures/result1-label.png}}}
    \qquad
    \begin{tabular}[b]{cc}\hline
      Table head & Table head \\ \hline
      Some values & Some values \\
      Some values & Some values \\
      Some values & Some values \\
      Some values & Some values \\
      Some values & Some values \\
      Some values & Some values \\ \hline
    \end{tabular}
    %\captionlistentry[table]{A table beside a figure}
    %\captionsetup{labelformat=andtable}
    %\caption{A table beside a figure}
\end{figure}

The second example exhibits a connected component containing $N = 21$ nodes, where all the three type of regulation are present. For this network we find the total of eleven fibers, where just six are fibers containing more than one node in it. As we can notice, for two arbitrary nodes be in the same fiber they must not just receive the same number of inward connections but the same number of each type of inward connections, this way receive the equivalent information from the rest of the network. We can see this for the example of the fibers $4$ e $5$, where even though both receives two links from the same central node, the fibers receives different types of information from that node, meaning that they are not the equivalent fibers.

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.3]{Figures/result2.png}
\end{figure}
\begin{figure}[H]
	\centering
	\includegraphics[scale=0.3]{Figures/result2-label.png}
\end{figure}

If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$. In cases like this the branching ratio of the fiber has a fractal value represented by a golden ratio $\phi_d$ resulted a loop information represented by a fibonacci sequence. This way, fiber $3$ can be classified by the values $| \phi_d, l = 2 \rangle$ where the fiber has two external regulator nodes. The fibration classification for the non-trivial fibers is showed in the table \ref{asdas}.

\begin{table}
\centering
\begin{tabular}[b]{cc}\hline
	Table head & Table head \\ \hline
	Some values & Some values \\
	Some values & Some values \\
	Some values & Some values \\
	Some values & Some values \\
	Some values & Some values \\
	Some values & Some values \\ \hline
  \end{tabular}
\end{table}

Before applying the algorithm for the whole network, we chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E. Coli} network. The same network is showed at the supplementary information from \cite{fibration2019}. The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in figure \ref{fig:result3-1}.

@@

The connected component showed at the figure \ref{fig:result3} is a representation of a component in the whole regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern. In the table X we give the classification for each fibration building block obtained for the whole bacteria network, including of course the fibers presented in the figure \ref{fig:result3-1}. In total, we have found $84$ non-trivial fiber groups containing a total of 462 nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data. To guarantee the correctness of the fiber distribution found we calculate after the application of the refinement partitioning algorithm the information received for each node inside a fiber and compares if each one process equivalent information.

The statistics concerning the number of each fibration block on the network is given in the table X, showing \textcolor{red}{describe the pattern of the statistics of the table that concerns the bacteria fiber statistics}.

\section{Conclusion}

>>>>

A network $G(V, E)$ is completely defined by the sets of the nodes elements $V$ and the set of the arcs $E$. The network has $N = |V|$ nodes that can have connections with one another defined by the set $E$, which contains $M = |E|$ ordered pair of nodes, denoting the directed links between the network nodes. Considering the network, we can define a graph partition $\bar{P}$ over $V$ as a set of pairwise disjoints subsets of $V$ whose union is all $V$, that is
\begin{equation}
	\bar{P} = \bigcup_{i} P_i
\end{equation}
where $P_i$ are the elements of the partition $\bar{P}$, called blocks. Considering this, if we take an additional graph partition $\bar{Q}$ that has the property that all of its blocks are contained in a block of $\bar{P}$, we say that $\bar{Q}$ is a refinement partition of $\bar{P}$.

@@

Finally, the complete algorithm to find the correct network fibers of a network $G(V, E)$ consists in initializing a graph partition $\bar{P}$ over all nodes from $V$ except the nodes that do not receive information from any other node, in which each one of these will be defined as isolated fibers already in the beginning of the algorithm. The partition $\bar{P}$ is defined as one block containing all the other nodes in the network. The algorithm maintains a queue $L$ of possible refinement sets, initially containing the single block of $\bar{P}$ and all the isolated blocks defined at the beginning. Then, we proceed as
\begin{quotation}
	\textbf{Coarsest Refinement Algorithm}: Remove from $L$ its first set $S$. Replace $\bar{P}$ by the \textit{I-split($S$, $\bar{P}$)}. Whenever a block $B \in \bar{P}$ splits into two or more nonempty blocks, add all but the largest to the back of $L$.
\end{quotation}
And this process is repeated until the queue $L$ is empty. At this point, the resulted partition $\bar{P}$ represents the coarsest input-tree stable partitioning of the network $G(V, E)$, where each block represents a network fiber with all its nodes having isomorphic input-trees. The figure \ref{fig:split} displays the splitting operation at the beginning of the refinement algorithm for a small network example.

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{Figures/test.png}
	\caption{A refinement step for the split function. Receiving the input partition $\bar{P}$ and a refinement set $S$, we identify the input-tree unstable blocks and split them into input-tree blocks with respect to $S$. Due to the refinement inheritance stability property, refining the resulted partition $\bar{P}$ with respect to other sets $S'$, that are not equal to $S$ or a union of already used sets $S$, guarantees the input-tree stability to $S$ during all the following algorithm steps.}
	\label{fig:split}
\end{figure}

@@

Next, I apply the above algorithm for the genetic regulatory network of the \textit{Escherichia Coli} bacteria. The obtention of this genetic network is through the transcriptional regulatory interaction data, where each gene is regulated by a transcription factor protein. Since a transcription factor in the cell is produced by a gene, it is possible to define directed relations between two genes if a gene is responsible for the production of a transcriptional factor, which regulates the other gene. Considering that a transcription factor can be either an activator(positive) or repressor(negative), or even behaves as both(dual), the directed links between genes can carry different types of information. Because of that, the partitioning algorithm must account for the type of message signals to construct appropriate stable input-trees for the network fibers. Therefore, for a proper application of the algorithm on the \textit{Escherichia Coli} genetic network, we label each node uniquely, either as numbers or string names, and also we do the same for each link with the type of connection between two genes.

Given the regulatory directed network $G(V, E)$ to be partitioned in fibers, it is very important for the correctness of the algorithm that the nodes that do not receive any information, that is, the nodes that do not have any inward connections, be preprocessing as isolated blocks in a different partition. This means that the initial graph partition $\bar{P}$ must be divided in two different partitions $\bar{P'}$ e $\bar{P''}$, where the first one should contains all the single-node blocks containing the solitaire nodes $v$ for which $| E^{-1}(\{v\}) | = 0$, and the second contains at the beginning of the algorithm a single block containing all the other nodes $w$ in which $| E^{-1}(\{w\}) | \geq 1$. The importance of this preprocessing is to guarantee that solitaire nodes do not be put on the same fibers during the refinement steps, since for any subset $S \subseteq V$, the solitaire nodes satisfies the equality $| E^{-1}(\{v\}) \cap S | = 0$. Furthermore, even though the blocks of $\bar{P'}$ are used as refinement sets, $\bar{P'}$ is not used by the split function in any step. This way, the final graph partition of $G(V, E)$ is the union of $\bar{P'}$ and the result of the refinement partitioning of $\bar{P''}$, that is, the coarsest or minimal input-tree stable partition of $G$.

After preprocessing the solitaire nodes, we have to define the data structures for the partition $\bar{Q}$ and its blocks $B$. We should define the implementation of a partition by a doubly-linked list of blocks, which allows that deletion of blocks be done in constante time $O(1)$ as long we have the block memory address during the procedure. A block is just a structure record containing indexing data along with a doubly-linked list containing all the nodes that belongs to it. Together with the queue of blocks $L$, these constructions are the main data structures necessary for an efficient implementation of the refinement partitioning algorithm. At the beginning of the algorithm, we enqueue all the blocks of $\bar{P'}$ e $\bar{P''}$ to $L$ (order is not important for the output correctness). Then, we start the algorithm initializing a partition $\bar{Q} = \bar{P''}$ and by removing the first element set $S$ of $L$, and we apply the \textit{I-split($S$, $\bar{Q}$)} function to identify the input-tree unstable blocks of $\bar{Q}$ and to split them into input-tree stable blocks with respect to $S$. After that, all the splitted blocks are pushed to the end of $L$, with exception the largest resulted blocks for each splitted block. As we have mentioned, the algorithm terminates when there is no more sets in $L$. This is the whole algorithm, even though the implementation of the \textit{I-split} function might not be so straightforward, since a given block $B$ can be splitted into an arbitrary number of blocks of different sizes. Considering this, I propose in the pseudocode \ref{alg:split} an efficient implementation construction to the splitting function.

\begin{algorithm}[t]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
	\Input{A set $S$ and a partition $\bar{Q}$}
    \Output{Input tree stable partition $\bar{Q}$ with respect to $S$}
	Initialize $\bar{U}$ as an empty partition\;
	\For{$\forall B \in \bar{Q}$}
	{
		\If{$\exists \ \{ w_i, w_j \} \subseteq B : | E^{-1}(\{w_i\})\cap S | \neq | E^{-1}(\{w_j\})\cap S |$}
		{
			\textit{push} $B$ to $\bar{U}$\;
			Initialize $\bar{T}$ as an empty partition\;
			\For{$\forall w_i \in B$}
			{
				\eIf{$\exists \ X \in \bar{T} : | E^{-1}(\{w_i\})\cap S | = X(E)$ }
				{
					insert $w_i$ in $X$\;

				}
				{
					create a new block $X$\;
					insert $w_i$ in $X$\;
					$X(E) \leftarrow | E^{-1}(\{w_i\})\cap S |$\;
					push block $X$ to $\bar{T}$ 
				}
			}
		}
		\textit{enqueue} all blocks $X \in \bar{T}$ in $L$, except the largest one\;
		\textit{copy} all blocks $X \in \bar{T}$ to $\bar{Q}$\;
	}
	\textit{delete} all blocks $B \in \bar{U}$ in $\bar{Q}$
	\caption{\textit{I-split} $(S,\bar{Q}, L)$}
	\label{alg:split}
\end{algorithm}

In the algorithm \ref{alg:split} above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output. Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$. This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}. In cases where the type of connections are non-trivial, i. e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network. For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.

Finally, considering all the discussion and implementation presented above, we can explicit the complete algorithm in just a few basic steps in algorithm \ref{alg:partitioning}.

A concrete implementation of the algorithm in a programming language is presented at the link \url{https://github.com/higorsmonteiro/fiberblocks} together with \textit{E. Coli} prepared data and another trial network examples. Further information about the application of the codes in other genetic regulatory network data can be found at the same link given.

\begin{algorithm}[h]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
	\Input{A network $G(V, E)$}
	%\KwResult{}
	Initialize $S$ as an empty set\;
	Initialize $L$ as an empty queue\;
	Initialize $\bar{P}$, $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
	$B' = \{ \{ w \} \in V : |E^{-1}(\{w\})|=0 \}$\;
	$B'' = \{ v \in V : |E^{-1}(\{v\})| \geq 1 \}$\;
	\textit{push} all $B'$ to $\bar{P'}$\;
	\textit{push} $B''$ to $\bar{P''}$\;
	\textit{enqueue} $B'' \in \bar{P''}$ to $L$\;
	\textit{enqueue} all blocks $B' \in \bar{P'}$ to $L$\;
	$\bar{Q} \leftarrow \bar{P''}$\;
	\While{$|L| \neq 0$}
	{
		$S \leftarrow \text{\textit{dequeue}}(L)$\;
		$\bar{Q} \leftarrow \text{\textit{I-input}}(S, \bar{Q}, L)$
	}
	\caption{Coarsest Refinement Graph Partitioning}
	\label{alg:partitioning}
\end{algorithm}

@@

Using the algorithm above, I applied it to a set of trial networks examples before its proper application to the \textit{Escherechia Coli} genetic regulatory network data. The reason for that is merely to show that the not just the algorithmic approach chosen is consistent but the written code per se is correctly implemented. For each network, I defined a adjacency list file containing all the directed connections between the nodes/genes and for each arc I have a string name defining the type of regulation of that specific link, where here, considering the genetic regulation context, the string types can be ''positive``, ''negative`` or ''dual``. The three trial examples are all small networks, the largest one containing a total of $48$ nodes and $77$ arcs, so that all can be used to test the correctness of the algorithmic approach applied. For these three examples we show the network drawing representation and their fibers distribution identified as the result of the refiniment partition.

The first example is showed at the figure \ref{fig:result1}. This network is disconnected, containing two main weakly connected components, and in addition contains only positive regulation between the interactions between the genes, showing the simpler case where the connections between nodes in a network are all of the same type. In this case, we find five non-trivial fibers, that is, fibers with size larger than one.

\begin{figure}[h]
	\centering
	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1.png}}}
	\qquad
	\subfloat[]{{\includegraphics[scale=0.3]{Figures/result1-1.png}}}
	\caption{First trial network example. Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected components, defined as the connected networks when we treat all the directed arcs as undirected edges. For each non-trivial fiber I give the same color for the nodes belonging to it.}
	\label{fig:result1}
\end{figure}

At the end of the algorithm, all the identified fibers are input-tree stable with respect to all fibers in the network, including the fiber itself. Then, by labelling each fiber with an index or color we can then construct the fibration building blocks through the calculation of the fundamental class number $n$ and through the subclass number $\ell$. Again, a fibration building block is defined as the nodes belonging to a fiber and all the $\ell$ external nodes that directly regulates at least one node of the current fiber. With that, we calculate the fundamental class number $n_k$ of the fiber $k$ by building the adjacency matrix $\mathbf{A}^{k}$ of its fibration building block and then calculating the largest eigenvalue of it. The value of $n$ quantifies the information cycles of the fibration building blocks and it can be either represent integer branching ratios or fractal golden ration of their input-tree topology class.

Labelling the resulted fiber distribution for the first example in figure \ref{fig:result1}, we obtain the following fibration classification for each fibratiion building block of the network containing more than one node:

\begin{figure}[!ht]
    \centering
    \subfloat[]{{\includegraphics[scale=0.22]{Figures/result1-label.png}}}
    \qquad
    \begin{tabular}[b]{cc}\hline
      Fiber & $| n, \ell \rangle$  \\ \hline
      1 & $| 0, 2 \rangle$ \\
      2 & $| 0, 1 \rangle$ \\
      3 & $| 0, 1 \rangle$ \\ 
      4 & $| 0, 1 \rangle$ \\
      5 & $| 0, 2 \rangle$ \\ \hline
	\end{tabular}
	\captionlistentry[table]{A table beside a figure}
    %\captionsetup{labelformat=andtable}
    \caption{A table beside a figure}
\end{figure}

The second example exhibits a connected component containing $N = 21$ nodes, where all the three type of regulation are present. For this network I find the total of eleven fibers, where only six are fibers containing more than one node in it. Important to note that for two arbitrary nodes be in the same fiber they must not just receive the same number of inward connections but the same number of each type of inward connections, receiving, this way, equivalent information from the rest of the network. We can see this for the example of the fibers $4$ e $5$, where even though both receives two links from the same central node, the fibers receives different types of information from that node, meaning that they are not equivalent fibers.

If we consider the fiber $3$, besides the inner autoregulation loop we have a loop information going outside the fiber and going back through an external regulator inside the fiber $1$. In cases like this the branching ratio of the fiber has a fractal value represented by a golden ratio $\phi_d$ resulted by a cycle of information represented by a fibonacci sequence. This way, fiber $3$ can be classified by the values $| \phi_d, \ell = 2 \rangle$ where the fiber has two external regulator nodes. The fibration classification for the non-trivial fibers is showed in the table \ref{tab:r2}.

%\begin{figure}[H]
%	\centering
%	\subfloat[]{{\includegraphics[scale=0.25]{Figures/result2.png}}}
%	\qquad
%	\subfloat[]{{\includegraphics[scale=0.25]{Figures/result2-label.png}}}
%	\caption{First trial network example. Containing a total of $N = 17$ nodes and $M = 22$ arcs, the network has two weakly connected %components, defined as the connected networks when we treat all the directed arcs as undirected edges. For each non-trivial fiber I %give the same color for the nodes belonging to it.}
%	\label{fig:result2}
%\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.3]{Figures/result2.png}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.3]{Figures/result2-label.png}
\end{figure}

\begin{table}[H]
\centering
\begin{tabular}[b]{cc}\hline
	Fiber & $| n, \ell \rangle$  \\ \hline
	1 & $| 0, 1 \rangle$ \\
	2 & $| 0, 1 \rangle$ \\
	3 & $| 0, 1 \rangle$ \\ 
	4 & $| 0, 1 \rangle$ \\
	5 & $| 0, 2 \rangle$ \\
	6 & $| 0, 2 \rangle$ \\ \hline
  \end{tabular}
  \caption{}
  \label{tab:r2}
\end{table}

Before applying the algorithm for the whole \textit{Escherichia Coli} network, I chose, for the finality of visualization and testing, to apply first the algorithm for a weakly connected component of the \textit{E. Coli} network. The same network is showed at the supplementary information of \cite{fibration2019}. The fiber distribution found is consistent with the one presented at \cite{fibration2019}, presenting the total of fifteen non-trivial fiber groups as shown in the figure \ref{fig:result3-1}.

@@

The connected component showed at the figure \ref{fig:result3} is a subset representation of the nodes of the regulatory network of the \textit{Escherichia Coli} bacteria and the resulted fibers shows just a portion of the whole fibers pattern. In the table X I provide the classification for each fibration building block obtained for the whole bacteria network, including, of course, the fibers presented in the figure \ref{fig:result3-1}. In total, I have found $84$ non-trivial fiber groups containing a total of $462$ nodes, obtaining a characteristic fiber statistics for the \textit{Escherichia Coli} network data. To guarantee the correctness of the fiber distribution found I calculated, after the refinement algorithm, the information received for each node inside the fibers and compares if each one process equivalent information. The result of this calculation is stored in the data file given at \url{https://github.com/higorsmonteiro/fiberblocks/blob/master/Data/fiberVerification.dat}, where for each node in a non-trivial fiber block I give the list of the nodes that sends information messages to the current node along with their fiber indexes and type of link values. Even though the algorithm implementation and the provided data above support the correctness of the results of this report, they shows a discrepancy comparing with the results exhibited at \cite{fibration2019} for the same regulatory network data.

The statistics concerning the fundamental class number and the external regulators of each fibration block on the network is given in the table X, showing \textcolor{red}{describe the pattern of the statistics of the table that concerns the bacteria fiber statistics}.
